Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs

### 2020-12-27 NEUROC/sec4-experiments.tex
更新section 4.

The main differences between training and inference were reflected in two aspects: the wall-clock time and the top time-consuming basic operators.
%
The inference time was much less than the training time.
%
Figure~\ref{fig:compare_wall_clock_time_of_training_and_inference} compares the wall-clock time of training and inference on the \texttt{amp}, \texttt{amc}, and \texttt{fli} datasets.
%
The results on the other datasets were similar.
%
Since the inference only conducted the forward propagation from the input layer to the prediction layer, the time of inference was very close to the time of the forward phase in training.
%
The inference time was 34\% (GCN), 32\% (GGNN), 25\% (GAT), and 32\% (GaAN) of the training time, averaged over all datasets.

>>>>

The main differences between training and inference were reflected in two aspects: the wall-clock time and the top time-consuming basic operators.
%
The inference time was much less than the training time.
%
Figure~\ref{fig:compare_wall_clock_time_of_training_and_inference} compares the wall-clock time of training and inference on the \texttt{amp}, \texttt{amc}, and \texttt{fli} datasets.
%
The results on the other datasets were similar.
%
Since the inference only conducted the forward propagation from the input layer to the prediction layer, the inference time was very close to the time of the forward phase in training.
%
The inference time was 34\% (GCN), 32\% (GGNN), 25\% (GAT), and 32\% (GaAN) of the training time, averaged over all datasets.
